---
title: "Quiz 1 Solution"
author: "Congye"
date: "10/13/2020"
output: pdf_document
---

- i. With $\Psi = 1$,
$$logf(x,\mu) = -(x - \mu) - exp\{-(x-\mu)\}$$
So
$$\textit{l}(\mu;x_{1},\cdots,x_{n} = n\mu - \sum^{n}_{i = 1}x_{i} - exp(\mu)\sum^{n}_{i=1}exp(-x_{i}))$$
```{r}
river <- c(50.4, 49.7, 49.9, 51.1, 49.2, 53.4, 51.1, 49.9, 51.3, 49.6)
ll_river <- function(theta, datavec) {
  n=length(datavec)
  s1=sum(datavec)
  s2=sum(exp(-datavec))
  return(n*theta-s1-exp(theta)*s2)
}
ll_river(48, river)
```
- ii. The score is- ii. The score is u($\mu$) =

$$\frac{\partial}{\partial \mu}\textit{l}(\mu;x_{1},\cdots,x_{n}) = n - exp(\mu)\sum_{i=1}^{n}exp(-x_{i}).$$
$u(\hat{\mu}) = 0 \Leftrightarrow$
$$
\begin{aligned}
\hat{\mu}  & = logn - log(\sum_{i=1}^{n}exp(-x_{i}))\\
& = -log(\frac{1}{n}\sum_{i=1}^{n}exp(-x_{i}))
\end{aligned}
$$
```{r}
n <- length(river)
s2 <- sum(exp(-river))
muhat = -log(s2 / n)
print(muhat)
```

- iii. 
$$l_{O}(\mu) = - \frac{\partial}{\partial\mu^{2}} - \frac{\partial}{\partial\mu} = exp(\mu)\sum_{i=1}^{n}exp(-x_{i}).$$
```{r}
IObs <- exp(muhat) * s2
print(IObs)
```
This is $n$, which is also obvious from part ii

- iv. $Var[\hat{\mu}] \approx 1/I_{O} = 0.1$
- v. Test is (a) one-tailed (asking wheter $\mu$ **exceeds** 50).
- vi. The Wald test statistic is
$$W = \frac{\hat{\mu} - 50}{se(\hat{\mu})}$$
```{r}
W = (muhat - 50) / sqrt(0.1)
print(W)
```
- vii. The p-value is $Pr[Z>W]=Pr[Z>0.3615794]$
```{r}
p = 1 - pnorm(W)
print(p)
```

- viii. Since $p > 0.05$ we (a) fail to reject the null hypothesis.

- ix. Evaluate the score at $\mu_{0} = 50$
```{r}
u_river <- function(theta, datavec) {
  n = length(datavec)
  s2 = sum(exp(-datavec))
  return(n - exp(theta) * s2)
}
u <- u_river(50, river)
u
```

- x. The $\chi^{2}$-distributed function of the score statistic using the information at $\mu_{0}$ is $U^{2} / I_{O}(\mu_{0})$
```{r}
u^2/10
```
For 20-21 only, because of an ambiguity in the original version of the question, I am also allowing:
```{r}
u / sqrt(10)
```

- xi. The p-value for the test is
```{r}
1 - pchisq(u^2/10, df=1)
```
- xii The alternative hypothesis is that (b) $\mu \neq \mu_{0}$
